---
title: "hddm predictive intervals"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
require(rethinking)
require(tidyverse)
require(patchwork)
```

# Import data
Read in Observed response data
```{r}
obs <- read_csv('choice_hddm.csv')
obs <- obs %>%
  mutate(rts = case_when(
    response == 0 ~ rt * -1,
    TRUE ~ rt
  ))
osubs <- sort(unique(obs$subj_idx))
orig <- vector(mode='list', length=length(osubs))
for (i in 1:length(osubs)) {
  orig[[i]] <- obs %>% 
    filter(subj_idx == osubs[i]) %>%
    select(rts) %>%
    pull()
}

obs_late <- read_csv('choice_hddm_late.csv')
obs_late <- obs_late %>%
  mutate(rts = case_when(
    response == 0 ~ rt * -1,
    TRUE ~ rt
  ))
osubs_late <- sort(unique(obs_late$subj_idx))
orig_late <- vector(mode='list', length=length(osubs_late))
for (i in 1:length(osubs_late)) {
  orig_late[[i]] <- obs_late %>% 
    filter(subj_idx == osubs_late[i]) %>%
    select(rts) %>%
    pull()
}
```

## Read in Posteriors
```{r}
params5 <- read_csv('c:/chddm/model5_params.csv',
               col_names=c('Param','mean','std',
                           'q2.5','q25','q50','q75','q97.5',
                           'mc_error'),
               skip = 1)
params5 %>% head()
```

```{r}
params5_late <- read_csv('c:/chddm/model5_late_params.csv',
               col_names=c('Param','mean','std',
                           'q2.5','q25','q50','q75','q97.5',
                           'mc_error'),
               skip = 1)
params5_late %>% head()
```

## Plot posteriors all trials
```{r}
v_sup <- params5 %>% filter(Param == 'v_support') %>%
  select(mean, q2.5, q97.5)
v_subs <- params5 %>% filter(str_detect(Param, 'v_support_subj')) %>%
  select(mean, q2.5, q97.5)
pdat1 <- tibble(
  Subject = 1:nrow(v_subs), Support = v_subs$mean,
  l = v_subs$q2.5, u = v_subs$q97.5,
  measure = rep('Drift Rate', nrow(v_subs)),
  avg = rep(v_sup$mean, nrow(v_subs)),
  avg_l = rep(v_sup$q2.5, nrow(v_subs)),
  avg_u = rep(v_sup$q97.5, nrow(v_subs))
)

p1 <- pdat1 %>% ggplot(aes(Subject, Support)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Drift Rate', title='Support') +
  ylim(-.2, .35) +
  theme_classic() 


v_mor <- params5 %>% filter(Param == 'v_moral') %>%
  select(mean, q2.5, q97.5)
v_subs <- params5 %>% filter(str_detect(Param, 'v_moral_subj')) %>%
  select(mean, q2.5, q97.5)
pdat2 <- tibble(
  Subject = 1:nrow(v_subs), Moral = v_subs$mean,
  l = v_subs$q2.5, u = v_subs$q97.5,
  measure = rep('Drift Rate', nrow(v_subs)),
  avg = rep(v_mor$mean, nrow(v_subs)),
  avg_l = rep(v_mor$q2.5, nrow(v_subs)),
  avg_u = rep(v_mor$q97.5, nrow(v_subs))
)

p2 <- pdat2 %>% ggplot(aes(Subject, Moral)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Drift Rate', title='Moral Conviction') +
  ylim(-.2, .35) +
  theme_classic() 


z_sup <- params5 %>% filter(Param == 'z_support') %>%
  select(mean, q2.5, q97.5)
z_subs <- params5 %>% filter(str_detect(Param, 'z_support_subj')) %>%
  select(mean, q2.5, q97.5)
pdat3 <- tibble(
  Subject = 1:nrow(z_subs), Support = z_subs$mean,
  l = z_subs$q2.5, u = z_subs$q97.5,
  measure = rep('Starting Bias', nrow(z_subs)),
  avg = rep(z_sup$mean, nrow(z_subs)),
  avg_l = rep(z_sup$q2.5, nrow(z_subs)),
  avg_u = rep(z_sup$q97.5, nrow(z_subs))
)

p3 <- pdat3 %>% ggplot(aes(Subject, Support)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Starting Bias') +
  ylim(-.05, .05) +
  theme_classic()


z_mor <- params5 %>% filter(Param == 'z_moral')  %>%
  select(mean, q2.5, q97.5)
z_subs <- params5 %>% filter(str_detect(Param, 'z_moral_subj')) %>%
  select(mean, q2.5, q97.5)
pdat4 <- tibble(
  Subject = 1:nrow(z_subs), Moral = z_subs$mean,
  l = z_subs$q2.5, u = z_subs$q97.5,
  measure = rep('Starting Bias', nrow(z_subs)),
  avg = rep(z_mor$mean, nrow(z_subs)),
  avg_l = rep(z_mor$q2.5, nrow(z_subs)),
  avg_u = rep(z_mor$q97.5, nrow(z_subs))
)

p4 <- pdat4 %>% ggplot(aes(Subject, Moral)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Starting Bias') +
  ylim(-.05, .05) +
  theme_classic()


a_sup <- params5 %>% filter(Param == 'a_support') %>%
  select(mean, q2.5, q97.5)
a_subs <- params5 %>% filter(str_detect(Param, 'a_support_subj')) %>%
  select(mean, q2.5, q97.5)
pdat5 <- tibble(
  Subject = 1:nrow(a_subs), Support = a_subs$mean,
  l = a_subs$q2.5, u = a_subs$q97.5,
  measure = rep('Boundary', nrow(a_subs)),
  avg = rep(a_sup$mean, nrow(a_subs)),
  avg_l = rep(a_sup$q2.5, nrow(a_subs)),
  avg_u = rep(a_sup$q97.5, nrow(a_subs))
)

p5 <- pdat5 %>% ggplot(aes(Subject, Support)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Boundary') +
  ylim(-.15, .15) +
  theme_classic()


a_mor <- params5_late %>% filter(Param == 'a_moral') %>%
  select(mean, q2.5, q97.5)
a_subs <- params5_late %>% filter(str_detect(Param, 'a_moral_subj')) %>%
  select(mean, q2.5, q97.5)
pdat6 <- tibble(
  Subject = 1:nrow(a_subs), Moral = a_subs$mean,
  l = a_subs$q2.5, u = a_subs$q97.5,
  measure = rep('Boundary', nrow(a_subs)),
  avg = rep(a_mor$mean, nrow(a_subs)),
  avg_l = rep(a_mor$q2.5, nrow(a_subs)),
  avg_u = rep(a_mor$q97.5, nrow(a_subs))
)

p6 <- pdat6 %>% ggplot(aes(Subject, Moral)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3)  +
  labs(y = 'Boundary') +
  ylim(-.15, .15) +
  theme_classic()
```

```{r}
patch <- (p1 | p2) /
  (p3 | p4) /
  (p5 | p6)

patch + plot_annotation(title='Model Posteriors')
ggsave('posteriors_model5.png', width=6, height=8)
```


## Plot posteriors later trials
```{r}
v_sup <- params5_late %>% filter(Param == 'v_support') %>%
  select(mean, q2.5, q97.5)
v_subs <- params5_late %>% filter(str_detect(Param, 'v_support_subj')) %>%
  select(mean, q2.5, q97.5)
pdat1_late <- tibble(
  Subject = 1:nrow(v_subs), Support = v_subs$mean,
  l = v_subs$q2.5, u = v_subs$q97.5,
  measure = rep('Drift Rate', nrow(v_subs)),
  avg = rep(v_sup$mean, nrow(v_subs)),
  avg_l = rep(v_sup$q2.5, nrow(v_subs)),
  avg_u = rep(v_sup$q97.5, nrow(v_subs))
)

p1_late <- pdat1_late %>% ggplot(aes(Subject, Support)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Drift Rate', title='Support') +
  ylim(-.2, .35) +
  theme_classic() 


v_mor <- params5_late %>% filter(Param == 'v_moral') %>%
  select(mean, q2.5, q97.5)
v_subs <- params5_late %>% filter(str_detect(Param, 'v_moral_subj')) %>%
  select(mean, q2.5, q97.5)
pdat2_late <- tibble(
  Subject = 1:nrow(v_subs), Moral = v_subs$mean,
  l = v_subs$q2.5, u = v_subs$q97.5,
  measure = rep('Drift Rate', nrow(v_subs)),
  avg = rep(v_mor$mean, nrow(v_subs)),
  avg_l = rep(v_mor$q2.5, nrow(v_subs)),
  avg_u = rep(v_mor$q97.5, nrow(v_subs))
)

p2_late <- pdat2_late %>% ggplot(aes(Subject, Moral)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Drift Rate', title='Moral Conviction') +
  ylim(-.2, .35) +
  theme_classic() 


z_sup <- params5_late %>% filter(Param == 'z_support') %>%
  select(mean, q2.5, q97.5)
z_subs <- params5_late %>% filter(str_detect(Param, 'z_support_subj')) %>%
  select(mean, q2.5, q97.5)
pdat3_late <- tibble(
  Subject = 1:nrow(z_subs), Support = z_subs$mean,
  l = z_subs$q2.5, u = z_subs$q97.5,
  measure = rep('Starting Bias', nrow(z_subs)),
  avg = rep(z_sup$mean, nrow(z_subs)),
  avg_l = rep(z_sup$q2.5, nrow(z_subs)),
  avg_u = rep(z_sup$q97.5, nrow(z_subs))
)

p3_late <- pdat3_late %>% ggplot(aes(Subject, Support)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Starting Bias') +
  ylim(-.05, .05) +
  theme_classic()


z_mor <- params5_late %>% filter(Param == 'z_moral')  %>%
  select(mean, q2.5, q97.5)
z_subs <- params5_late %>% filter(str_detect(Param, 'z_moral_subj')) %>%
  select(mean, q2.5, q97.5)
pdat4_late <- tibble(
  Subject = 1:nrow(z_subs), Moral = z_subs$mean,
  l = z_subs$q2.5, u = z_subs$q97.5,
  measure = rep('Starting Bias', nrow(z_subs)),
  avg = rep(z_mor$mean, nrow(z_subs)),
  avg_l = rep(z_mor$q2.5, nrow(z_subs)),
  avg_u = rep(z_mor$q97.5, nrow(z_subs))
)

p4_late <- pdat4_late %>% ggplot(aes(Subject, Moral)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Starting Bias') +
  ylim(-.05, .05) +
  theme_classic()


a_sup <- params5_late %>% filter(Param == 'a_support') %>%
  select(mean, q2.5, q97.5)
a_subs <- params5_late %>% filter(str_detect(Param, 'a_support_subj')) %>%
  select(mean, q2.5, q97.5)
pdat5_late <- tibble(
  Subject = 1:nrow(a_subs), Support = a_subs$mean,
  l = a_subs$q2.5, u = a_subs$q97.5,
  measure = rep('Boundary', nrow(a_subs)),
  avg = rep(a_sup$mean, nrow(a_subs)),
  avg_l = rep(a_sup$q2.5, nrow(a_subs)),
  avg_u = rep(a_sup$q97.5, nrow(a_subs))
)

p5_late <- pdat5_late %>% ggplot(aes(Subject, Support)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3) +
  labs(y = 'Boundary') +
  ylim(-.15, .15) +
  theme_classic()


a_mor <- params5_late %>% filter(Param == 'a_moral') %>%
  select(mean, q2.5, q97.5)
a_subs <- params5_late %>% filter(str_detect(Param, 'a_moral_subj')) %>%
  select(mean, q2.5, q97.5)
pdat6_late <- tibble(
  Subject = 1:nrow(a_subs), Moral = a_subs$mean,
  l = a_subs$q2.5, u = a_subs$q97.5,
  measure = rep('Boundary', nrow(a_subs)),
  avg = rep(a_mor$mean, nrow(a_subs)),
  avg_l = rep(a_mor$q2.5, nrow(a_subs)),
  avg_u = rep(a_mor$q97.5, nrow(a_subs))
)

p6_late <- pdat6_late %>% ggplot(aes(Subject, Moral)) +
  geom_point(size=2, color=rangi2) +
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), linetype='dashed') +
  geom_hline(yintercept=0, alpha=.3)  +
  labs(y = 'Boundary') +
  ylim(-.15, .15) +
  theme_classic()
```

```{r}
patch_late <- (p1_late | p2_late) /
  (p3_late | p4_late) /
  (p5_late | p6_late)

patch_late + plot_annotation(title='Model Posteriors')
ggsave('posteriors_model5_late.png', width=6, height=8)
```



```{r}
plot_dat <- bind_rows(pdat1, pdat2, pdat3,
                      pdat4, pdat5, pdat6) %>%
  mutate(Estimate = case_when(
    is.na(Support) ~ Moral,
    TRUE ~ Support)
  ) %>% 
  mutate(IV = case_when(
    is.na(Support) ~ 'Moral',
    TRUE ~ 'Support'
  ))

plot_dat$measure <- 
  factor(plot_dat$measure,
         levels=c('Boundary', 'Starting Bias', 'Drift Rate'))
plot_dat$IV <-
  factor(plot_dat$IV,
         levels=c('Support', 'Moral'))

plot_dat %>% ggplot(aes(Subject, Estimate)) +
  geom_point(size=2, color=rangi2) + 
  geom_errorbar(aes(ymin=l, ymax=u)) +
  geom_line(aes(y=avg), alpha=.8, linetype='dashed') +
  geom_hline(yintercept=0, alpha=.5) +
  theme_classic() + 
  facet_wrap(measure ~ IV, ncol=2, scales='free_y')
```
## Read in posterior predictive data

### For all trials
Read in predictions from hddm models
```{r}
s1 <- read_csv('c:/chddm/model1_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
# Sample the id of the simulated data set (1 per simulation, 0..499)
# SimID is id of the resp within a simulated set (1 per resp)
s1 %>% head()
s2 <- read_csv('c:/chddm/model2_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
s3 <- read_csv('c:/chddm/model3_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
s4 <- read_csv('c:/chddm/model4_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
s5 <- read_csv('c:/chddm/model5_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
```

Helper functions for extracting samples and plotting observed vs predicted
```{r}
sample_subject <- function(d, n_sim=20) {
  samps <- unique(d$Sample)
  resps <- unique(d$SimID)
  
  out <- matrix(0, nrow=length(resps), ncol=n_sim)
  ids <- sample(samps, n_sim)
  for (i in 1:n_sim) {
    out[,i] <- d %>% filter(Sample == ids[i]) %>% select(RT) %>% pull()
  }
  return(out)
}

plot_preds <- function(orig, sims, n_sim=20) {
  subs <- unique(sims$Subject)
  pulls <- vector(mode='list', length=length(subs))
  
  for (i in 1:length(subs)) {
    d <- sims %>%
      filter(Subject == subs[i])
    pulls[[i]] <- sample_subject(d, n_sim)
  }
  
  n_subs <- length(subs)
  
  par(mfrow=c(3,3))
  for (i in 1:n_subs) {
    #rtm <- max(abs(range(orig[[i]])))
    if (i == 1) 
      ymax = 2.0
    else
      ymax = 0.35
    dens(orig[[i]], col=rangi2, xlim=c(-6,6), ylim=c(0,ymax),
         lwd=2, main = paste0('Subject ',i))
    for (j in 1:n_sim) 
      dens(pulls[[i]][,j], add=TRUE, col=grau(alpha=.2))
  }
}

rts2mat <- function(d, subject) {
  m <- s1 %>%
    filter(Subject == subject)%>% 
    pivot_wider(names_from=Sample, values_from = 'RT') %>% 
    select(-Subject) %>% select(-SimID) %>% 
    as.matrix(nrow=100)
  return(m)
}

```

#### Model 1
`v ~ 1 + support`
`z ~ 1 + moral`
```{r}
png('model1_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s1, n_sim=30)
dev.off()
```

#### Model 2
`v ~ 1 + support`
`a ~ 1 + moral`
```{r}
png('model2_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s2, n_sim=30)
dev.off()
```

#### Model 3
`v ~ 1 + support + moral`
```{r}
png('model3_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s3, n_sim=30)
dev.off()
```

#### Model 4
`v ~ 1 + support`
```{r}
png('model4_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s4, n_sim=30)
dev.off()
```

#### Model 5
`v ~ 1 + support + moral`
`a ~ 1 + support + moral`
`z ~ 1 + support + moral`
```{r}
png('model5_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s5, n_sim=30)
dev.off()
```


### For late trials

```{r}
s2late <- read_csv('c:/chddm/model2_late_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))

s5late <- read_csv('c:/chddm/model5_late_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
```


#### Model 2
`v ~ 1 + support`
`a ~ 1 + moral`
```{r}
png('model2_late_preds.png', width=800, height=800, res = 120)
plot_preds(orig_late, s2late, n_sim=30)
dev.off()
```

#### Model 5
`v ~ 1 + support + moral`
`a ~ 1 + support + moral`
`z ~ 1 + support + moral`
```{r}
png('model5_late_preds.png', width=800, height=800, res = 120)
plot_preds(orig_late, s5late, n_sim=30)
dev.off()
```


# Repeat with only unambiguous preferences
(i.e. where $Support_{Left} \neq Support_{Right}$)


# Import data
Read in Observed response data
```{r}
obs <- read_csv('choice_hddm_unambig.csv')
obs <- obs %>%
  mutate(rts = case_when(
    response == 0 ~ rt * -1,
    TRUE ~ rt
  ))
osubs <- sort(unique(obs$subj_idx))
orig <- vector(mode='list', length=length(osubs))
for (i in 1:length(osubs)) {
  orig[[i]] <- obs %>% 
    filter(subj_idx == osubs[i]) %>%
    select(rts) %>%
    pull()
}
```

Read in predictions from hddm models
```{r}
s1 <- read_csv('c:/chddm/ua_model1_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
# Sample the id of the simulated data set (1 per simulation, 0..499)
# SimID is id of the resp within a simulated set (1 per resp)
s1 %>% head()
s2 <- read_csv('c:/chddm/ua_model2_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
s3 <- read_csv('c:/chddm/ua_model3_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
s4 <- read_csv('c:/chddm/ua_model4_samples.csv', 
               col_names = c('Subject', 'Sample', 'SimID', 'RT'),
               skip = 1, col_types = cols(
                 .default=col_double(),
                 Subject = col_character()
               ))
```

## Model 1
`v ~ 1 + support`
`z ~ 1 + moral`
```{r}
png('ua_model1_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s1, n_sim=30)
dev.off()
```

## Model 2
`v ~ 1 + support`
`a ~ 1 + moral`
```{r}
png('ua_model2_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s2, n_sim=30)
dev.off()
```

## Model 3
`v ~ 1 + support + moral`
```{r}
png('ua_model3_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s3, n_sim=30)
dev.off()
```

## Model 4
`v ~ 1 + support`
```{r}
png('ua_model4_preds.png', width=800, height=800, res = 120)
plot_preds(orig, s4, n_sim=30)
dev.off()
```





```{r}
n_sim <- 20

subs <- unique(s1$Subject)

pulls <- vector(mode='list', length=length(subs))
for (i in 1:length(subs)) {
  d <- s1 %>% filter(Subject == subs[i])
  pulls[[i]] <- sample_subject(d, n_sim)
}
```


```{r}
n_subs <- length(subs)

par(mfrow=c(3,3))
for (i in 1:n_subs) {
  rtm <- max(abs(range(orig[[i]])))
  dens(orig[[i]], col=rangi2, xlim=c(-rtm,rtm), ylim=c(0,3/rtm),
       lwd=3, main = paste0('Subject ',i))
  for (j in 1:n_sim) 
    dens(pulls[[i]][,j], add=TRUE, col=grau(alpha=.25))
}
```


```{r}


```


```{r}
sub1 <- s1 %>% 
  filter(Subject == 'wfpt.0')
sub1rts <- sample_subject(sub1, n_sim)

plot(NULL, xlim=c(-2,2), ylim=c(0,2), xlab="RT", ylab="Density")
for (i in 1:n_sim)
  dens(sub1rts[,i], add=TRUE, col=grau(alpha=.3))
```

